---
title: "HW5 -- Ying Zheng"
output:
  pdf_document: default
  html_notebook: default
---
Problem 1 
```{r load_packages, include=FALSE}
library(vars)
library(portes)
```
(a)
```{r}
data= read.table("MacroVars.csv",sep=",", header=T)
acf(data)
```
```{r}
```
Comments:
The plots above showed us acf and ccf of the 3 macro variables GDP, FFR and CPI. On the diagoanl are acfs of them, and the rest are ccfs. We notice that GDP is correlated with FFR at lag 0, -1, -5 and -10, while it has barely any correlation with CPI at all lags. FFR has barely any correlation with CPI at all lags either.
```{r}
```
(b)
```{r}
holdfit = VAR(data, lag.max=20)
holdfit$p
```
```{r}
```
(c)
```{r}
serial.test(holdfit)
```
The p-value is 0.02528, which is smaller than 0.05, shows evidence of serial correlation in residuals.
```{r}
```
Problem 2 (a)
```{r}
TbGdpPi = read.csv("TbGdpPi.csv", header=TRUE)
TbPi.diff = ts(apply(TbGdpPi[,-2],2,diff), start=c(1955,2), freq=4)
plot(TbPi.diff)
acf(TbPi.diff^2)
source("SDAFE2.R")
mLjungBox(TbPi.diff^2, lag=8)
```
```{r}
```
Yes. First, the plots above shows clustering effects. Secondly, from the Ljung-Box test, there is strong evidence of correlation in the joint series. Finally, from the plot of TbPi.diff, we can see unstationarity. So it exhibit conditional heteroskedasticity.
```{r}
```
(b)
```{r}
EWMA.param = est.ewma(lambda.0=0.95, innov=TbPi.diff)
EWMA.param$lambda.hat
EWMA.Sigma=sigma.ewma(lambda=EWMA.param$lambda.hat,innov=TbPi.diff)
par(mfrow = c(2,2))
plot(ts(EWMA.Sigma[1,1,]^.5, start = c(1955, 2), frequency = 4),
     type = 'l', xlab = "year", ylab = NULL,
     main = expression(paste("(a) ", hat(sigma)["1,t"])))
plot(ts(EWMA.Sigma[1,2,], start = c(1955, 2), frequency = 4),
     type = 'l', xlab = "year", ylab = NULL,
     main = expression(paste("(b) ", hat(sigma)["12,t"])))
plot(ts(EWMA.Sigma[1,2,]/(sqrt(EWMA.Sigma[1,1,]* EWMA.Sigma[2,2,])),
        start = c(1955, 2), frequency = 4),
     type = 'l', xlab = "year", ylab = NULL,
     main = expression(paste("(c) ", hat(rho)["12,t"])))
plot(ts(EWMA.Sigma[2,2,]^.5, start = c(1955, 2), frequency = 4),
     type = 'l', xlab = "year", ylab = NULL,
     main = expression(paste("(d) ", hat(sigma)["2,t"])))
```
```{r}
```
From the estimates above, the estimated parameter is 0.8665812.
```{r}
```
(c)
```{r}
n = dim(TbPi.diff)[1]
d = dim(TbPi.diff)[2]
stdResid.EWMA = matrix(0,n,d)
for(t in 1:n){
  stdResid.EWMA[t,] = TbPi.diff[t,] %*% matrix.sqrt.inv(EWMA.Sigma[,,t])
}
mLjungBox(stdResid.EWMA^2, lag=8)
```
Form the Ljung-Box test of the squared standardized residuals, the p-value is 0.002, which is significantly smaller than 0.05, showing strong evidence of serial correlation. So the EWMA model is not adequate.