---
title: "Homework2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(glmnet)
```
Problem 2
(a)
```{r}
data = read.table('trends_train.csv', sep = ",",header=TRUE)
data$Week = as.Date(as.character(data$Week), format = "%Y-%m-%d")
#class(data$Week)
search.vol = data.frame(data[,2:(ncol(data)-1)])
#check
colnames(search.vol[96]) == colnames(data[97])

fit_lasso = glmnet(as.matrix(search.vol),as.matrix(data$logret),family='gaussian',alpha=1)
#fit_lasso$lambda
plot(fit_lasso,xvar='lambda')
```
(b)
```{r}
cv_lasso = cv.glmnet(as.matrix(search.vol),as.matrix(data$logret),family='gaussian',alpha=1)
names(cv_lasso)
plot(cv_lasso)

#We can pull out the mean, sd, upper, and lower bounds with
cmv = cv_lasso$cvm
cvup = cv_lasso$cvup
cvlo = cv_lasso$cvlo
#so we can make pretty custom plots, like
plot(log(cv_lasso$lambda),cv_lasso$cvm,ylim=c(min(cv_lasso$cvlo),max(cv_lasso$cvup)),type='l')
polygon(c(log(cv_lasso$lambda),rev(log(cv_lasso$lambda))),c(cv_lasso$cvup,rev(cv_lasso$cvlo)),col='grey',border=NA)
lines(log(cv_lasso$lambda),cv_lasso$cvm)
```
```{r}
cv_lasso = cv.glmnet(as.matrix(search.vol),as.matrix(data$logret),family='gaussian',alpha=1)

#we can also directly access the chosen values of lambda
Lambda.min = cv_lasso$lambda.min
Lambda.1se = cv_lasso$lambda.1se

#Number of predictor when Lambda is the minimum
sum(as.logical(coef(fit_lasso,s=Lambda.min)))

#Number of predictor when Lambda is 1se
sum(as.logical(coef(fit_lasso,s=Lambda.1se)))
```
(c) Number of predictor when we choose Lambda.min is greater than the number of predictor if we choose Lambda.1se. The nonzero coefficients we have are `r sum(as.logical(coef(fit_lasso,s=Lambda.min))) - 1` when we choose Lambda.min and  `r sum(as.logical(coef(fit_lasso,s=Lambda.1se))) - 1 ` when we choose Lambda.1se. Thus, the amount of true signals of this model is way less then 98.
```{r}
set.seed(1)
yhat_lasso = predict(fit_lasso,newx=as.matrix(search.vol),s=Lambda.min)
plot(data$logret,yhat_lasso,main="Scatterplot of Yhat vs. True Y",
   xlab="True log return ", ylab="Lasso log return ", pch=19)
#abline(h=mean(yhat_lasso),v=mean(data$logret),col="blue")
abline(0,1, col="red")
mean((yhat_lasso-data$logret)^2)
```
(d) The points scatter along the Y = X line, but with large variance. 
```{r}
set.seed(1)
for (i in 1:nrow(data)){
  yhat_i = predict(fit_lasso,newx=as.matrix(search.vol[i,]),s=Lambda.min)
  if (yhat_i >= 0){
    data$expret[i] = data$logret[i]
  }else{
    data$expret[i] = - data$logret[i]
  }
  #print(yhat_i)
}
sum(data$expret)
sum(data$logret)
```
(e) My sum of log return of the strategy is `r sum(data$expret)`, while the return I would have realized if I bought on the first day of the and sold on the last day is `r sum(data$logret)` My strategy triumphs. 
```{r}
set.seed(1)
test = read.table('trends_test.csv', sep = ",",header=TRUE)
yhat_lasso_test = predict(fit_lasso,newx=as.matrix(test[,2:(ncol(test)-1)]),s=Lambda.min)
plot(test$logret,yhat_lasso_test,main="Scatterplot of Yhat vs. True Y",
   xlab="True log return ", ylab="Lasso log return ", pch=19)
#abline(h=mean(yhat_lasso),v=mean(data$logret),col="blue")
abline(0,1, col="red")

test_search = test[,2:(ncol(test)-1)]

for (i in 1:nrow(test)){
  yhat_i = predict(fit_lasso,newx=as.matrix(test_search[i,]),s=Lambda.min)
  if (yhat_i >= 0){
    test$expret[i] = test$logret[i]
  }else{
    test$expret[i] = - test$logret[i]
  }
  #print(yhat_i)
}
sum(test$expret)
sum(test$logret)
```
(f) My sum of log return of the strategy is`r sum(test$expret)` , while the return I would have realized if I bought on the first day of the and sold on the last day is `r sum(test$logret)`. My strategy works bad on test data.  